Theories of deliberated choice

### 2022-08-15 simple.tex
Update on Overleaf.

\subsection{Argumentative theories of deliberated choice}
\label{sec:dynamic}
An argumentative theory of deliberated choice $\gamma$ is defined as a tuple $(\pga, \arga, \dg)$, where $\pga \in P$ is the proposition supported by the theory, $\arga \in \allargs$ is the initial argument in favor of $\pga$ and $\dg$ is a defense relation.
\commentYM{puisque la théorie empirique est une théorie empirique D'UNE CERTAINE THEORIE NORMATIVE, je m'attendrais  à ce qu'on voit apparaître la théorie normative dans la formule de la théorie empirique, non ?}

@@

This mechanism permits to define defenders of defenders of an argument, $\dg(\dg(\ar))$, defenders of defenders of defenders of an argument, … This yields the following notion of depth.
Given any set $S$ and function $f: S → S$, let $f^0$ represent the identity function, and given $k \in \N$, let $f^{k + 1} = f \circ f^k$.
The bounded depth condition on the defense relation imposes that
$\exists k \in \N^* \suchthat (\dg)^k(\arga) = \emptyset$.
The smallest such $k$ is called the depth of the theory.
\commentYM{ok soit, ça semble raisonnable, mais tu n'as pas de raison plus forte, j'adopterais une formulation plus modeste et ouverte, du genre "ça semble souhaitable"}

>>>>

\subsection{Argumentative theories of deliberated choice}
\label{sec:dynamic}
An argumentative theory of deliberated choice $\gamma$ is defined as a tuple $(\pga, \arga, \dg)$, where $\pga \in P$ is the proposition supported by the theory, $\arga \in \allargs$ is the initial argument in favor of $\pga$ and $\dg$ is a defense relation.

@@

This mechanism permits to define defenders of defenders of an argument, $\dg(\dg(\ar))$, defenders of defenders of defenders of an argument, … This yields the following notion of depth.
Given any set $S$ and function $f: S → S$, let $f^0$ represent the identity function, and given $k \in \N$, let $f^{k + 1} = f \circ f^k$.
The bounded depth condition on the defense relation imposes that
$\exists k \in \N^* \suchthat (\dg)^k(\arga) = \emptyset$.
The smallest such $k$ is called the depth of the theory.
